Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-02 paper.tex
Add mesh figs
Add 2-D vorticity figure and discuss benefits of CFD interpolation

It is assumed that if the turbine power output and near-wake predictions from
the numerical model match those of the experiments, that the flow field can be
inspected in greater detail, i.e., that the experiments will have been
``interpolated''. This will allow us to see where the dominant flow structures
originate and help develop low-order wake generator models for use in turbine
array modeling. For example, Araya et al. modeled the flow through a VAT array
using leaky Rankine bodies \cite{Araya2014}. Shamsoddin and Porte-Agel modeled a
2-D CFT using large eddy simulation (LES) with an actuator line approach to
impart force on the flow field \cite{Shamsoddin2014}.

@@

\begin{figure}[ht]
    \caption{Overview of the 2-D computational mesh.}

@@

\begin{figure}[ht]
    \caption{Detailed view of the 2-D computational mesh near the blades.}

@@

>>>>

It is assumed that if the turbine power output and near-wake predictions from
the numerical model match those of the experiments, that the flow field can be
inspected in greater detail, i.e., that the experiments will have been
``interpolated''. This will give us access to unmeasured quantities, e.g.
pressure, and allow us to see where the dominant flow structures originate and
help develop low-order wake generator models for use in turbine array modeling.
For example, Araya et al. modeled the flow through a VAT array using leaky
Rankine bodies \cite{Araya2014}. Shamsoddin and Porte-Agel modeled a 2-D CFT
using large eddy simulation (LES) with an actuator line approach to impart force
on the flow field \cite{Shamsoddin2014}.

@@

\begin{figure}[ht]    
    \includegraphics[width=0.8\textwidth]{figures/2d_mesh}

    \caption{Overview of the 2-D computational mesh.}

@@

\begin{figure}[ht]
    \includegraphics[width=0.7\textwidth]{figures/2D_blade_mesh_closeup}

    \caption{Detailed view of the 2-D computational mesh near the blades.}

@@

Visualizing the complicated wake generated by the turbine is presented for the
2-D and 3-D Spalart--Allmaras cases in Figure~\ref{fig:vorticity-3D} and
Figure~\ref{fig:vorticity-3D}, respectively. It can be seen how the upstream
blade---as it turns back into the streamwise direction---is shedding a large
amount of spanwise vorticity due to the separated flow. In the 3-D case, strong
tip vortices are also present, which trace the ``contracting'' wake flow on the
$-y$ side of the turbine associated with the induced vertical velocity field.

\begin{figure}
    \includegraphics[width=0.65\textwidth]{figures/2D_vorticity_SA_964}

    \caption{Instantaneous vorticity contours (at $t=9.64$ s) computed for the
        2-D Spalart--Allmaras case.}

    \label{fig:vorticity-2D}
\end{figure}

\begin{figure}
    \caption{Iso-vorticity contours colored by the streamwise component of
        vorticity for the 3-D Spalart--Allmaras case.}

    \label{fig:vorticity-3D}
\end{figure}
